\chapter{System Goals and Requirements}


\section{Transmission}

For successful clutch operations, \citet{clutch_control} quantify two requirements to be satisfied by any clutch controller:
\begin{itemize}
  \item a \emph{no-kill} condition, whereby the engine speed must remain above a certain value, $\omega_e^{min}$, and
  \item a no-lurch condition which states that the derivative of the clutch slip $\dot{\omega}_{s1}=\dot{\omega}_e-\dot{\omega}_c$ at the moment of full engagement is near zero. This means the car doesn't jerk or lurch forward, and is a more important requirement when crawling than launching.
\end{itemize}



\subsection{Shift Speed}

Improve shift speed and smoothness, 50 ms to upshift, 100 ms to downshift.


\subsection{Launch Control}

Provide launch control, decrease launch time and wheel slippage by
xxx.


\subsection{Neutral Find}

Decrease time required to find neutral, worst case is 500 ms.


\subsection{Anti-Stall}

Implement anti-stall feature, avoid stalling in any gear in spin-out
situations etc.


\subsection{Electropneumatics}

Reduce air consumption by 50\%, improve reliability. 


\section{Intake}

Implement variable-length (2-stage intake) within 150 ms to gain a
power advantage of xxx ftlbs torque over previous.

Automatically optimize runner length by monitoring throttle position,
engine RPM data from ECU.


\section{Starter}

Implement dual-mode starting system, including manual and one-touch.

Provide at least 5A of current for 30 seconds to starter solenoid.


\section{Braking}


\subsection{Bias Adjustment}

Eliminate manual adjustment by implementing an electronic adjustment
capability. 

Actuate a 4-wire stepper motor attached to the brake pedal assembly.

Be able to actuate bias from the cockpit electronically from 30/70
to 70/30 by steps of 1/2\% in less than one second while vehicle in
motion.

Lock out bias adjustment while braking.


\subsection{Calibration}

Must provide ability to recalibrate adjustment systems to adjust for
mechanical wear and inconsistency. Calibration routines should take
no longer than 30 seconds. 


\input{goals_and_requirements/goals_and_requirements_telemetry.tex}


\section{Driver Interface}


\subsection{Driver Controls}

Provide a means of shifting gears with minimum driver effort. (No
manual timing or clutching)

Provide a means of actuating all the features of the transmission
system (....)


\subsection{Vehicle Dynamic Adjustment}

Provide an easy to use interface to adjust vehicle dynamic parameters.

Allow driver to choose between sets of dynamic vehicle parameters
or `operating modes'.

Adjustment should be made by a single knob to reduce driver effort
required.

Adjustment of any vehicle parameters is verboten above 25 km/h.

Tuning of individual dynamic parameters and permanent changing of
preset modes should be capable through the driver interface itself.


\subsection{Diagnostic Information}

Critical warnings (....) must be delivered to the driver on an easy-to-read
display.

Supplimentary vehicle performance information should be available
to the driver (engine RPM, fuel, oil pressure, battery voltage, etc.)
without being a distraction.


\subsection{Visually Appealing Interface}

Display startup logo.

Display easy-to-read fonts.

Interface should never be a distraction to the driver.

Visible in full light as well as low light.

Visible through sun visor helmet.


\section{Electrical System and Harness}

Minimize wiring, noise resiliance, maximise interconnectivity

power usage