\chapter{Attached Materials}

Included with this report is a DVD containing material relevant to the project. This material includes:

\begin{itemize}
	\item the \emph{source code} for the various modules, libraries, and test harnesses; 
	\item the \emph{hardware schematics} and \emph{printed circuit board layouts} for the four modules; and
	\item the \emph{Simulink models} for the electro-pneumatic system.
\end{itemize}

\section*{Source Code}

The complete source code for the project is included in the \texttt{source\_code} directory. Consult Appendix \ref{apx:environment} for a detailed description of the build environment for the source code. Table \ref{tbl:attached_source_code} lists the source code included on the DVD.

\begin{table}[H]
\caption{Description of source code included on the DVD.}
\centering
\begin{tabular}{|c|l|}
	\hline 
	Directory & Contents \\ 
	\hline
	\hline
	\texttt{cantester} & CAN diagnostic tool and input examples. \\
	\hline	
	\texttt{canping168} & {}Automatic CAN packet reply utility. \\
	\hline	
	\texttt{helloc128} & {}``Hello World'' LED-blinker for the AT90CAN128. \\ 
	\hline		
	\texttt{libadc} & Library for the on-board ADC. \\ 
	\hline		
	\texttt{libcan} & Library for the on-board CAN controller. \\ 
	\hline
	\texttt{libeeprom} & Library for the on-board EEPROM. \\ 
	\hline		
	\texttt{libracetech} & Library for the RaceTech DAC packet injection and decoding. \\ 
	\hline		
	\texttt{libspi} & Library for the onboard SPI interface. \\ 
	\hline	
	\texttt{libxbee} & Library for the XBee Pro wireless modem.  \\ 
	\hline	
	\texttt{pbr\_braking} & Brake module software. \\ 
	\hline
	\texttt{pbr\_engine} & Engine and transmission module software. \\ 
	\hline	
	\texttt{pbr\_telemetry} & Telemetry module software. \\ 
	\hline	
	\texttt{pbr\_steering} & Driver interface software. \\ 
	\hline	
\end{tabular}
\label{tbl:attached_source_code}
\end{table}

\section*{Schematics and Layouts}

The hardware schematics and circuit board layouts are included in the \texttt{schematics} directory. Consult Appendix \ref{apx:environment} for a detailed description of the software used to develop the schematics and layouts. Table \ref{tbl:attached_schematics} lists the schematics  and layouts included on the DVD.

\begin{table}[H]
\caption{Description of schematics and layouts included on the DVD.}
\centering
\begin{tabular}{|c|c|c|c|}
	\hline 
	Directory & Module & Schematic File & Layout File \\ 
	\hline
	\hline
	\texttt{brake} & Braking  & \texttt{brake.sch} & \texttt{brake.brd} \\
	\hline	
	\texttt{engine} & Engine and Transmission & \texttt{engine.sch} & \texttt{engine.brd} \\
	\hline	
	\texttt{telemetry} & Telemetry & \texttt{telemetry.sch} & \texttt{telemetry.brd} \\
	\hline	
	\texttt{steering} & Driver Interface & \texttt{steering.sch} & \texttt{steering.brd} \\			
	\hline	
\end{tabular}
\label{tbl:attached_schematics}
\end{table}

\section*{Simulink Models}

The Simulink models used to develop the electro-pneumatic system are included in the \texttt{simulink} directory. They were developed with the Simulink tool-kit included with MATLAB release ``2008b''.
