\chapter{Subsystem Implementation\label{cha:implementation}}

The purpose of this chapter is to document the work completed in the implementation phase of the project. Implementation was carried out with three major goals in mind:

\begin{enumerate}
  \item To verify the system design, and compare the results with those desired in Ch. \ref{cha:goals};
  \item To use the results as working prototypes for the demonstration and communication of various aspects of the project; and
  \item To produce a first iteration of usable modules to be integrated into the vehicle for competition in May of 2010.
\end{enumerate}

This chapter is broken down into eight sections. First, the simulation and physical implementation of the electro-pneumatic subsystem is discussed. Next, commonalities in the hardware and software implementations are introduced. Then, the hardware and software implementations of the four modules are explained. Finally, the \emph{CAN Diagnostic Tool} is introduced. This tool was implemented to allow for in-place testing of the four modules, and is complex enough to warrant inclusion in the implementation.

\input{implementation/implementation_pneumatic}
\input{implementation/implementation_hardware_common}
\input{implementation/implementation_software_common}
\input{implementation/implementation_engine_transmission}
\input{implementation/implementation_braking}
\input{implementation/implementation_telemetry}
\input{implementation/implementation_driver_interface}
\input{implementation/implementation_can_tester}