%%% Shorten the running head so it doesn't collide in this chapter...
\fancyhead[L]{Automotive Network}

\chapter{Conclusions and Recommendations}

This chapter will outline the contributions of the project and summarize what was accomplished. Recommendations for future work for each of the four modules will also be made.

\section{Conclusions}

In this thesis we have discussed the goals, designs, and implementations of a network of four modules for the 2010 Formula SAE vehicle.

\begin{itemize}

  \item A novel pneumatic design was proposed to improve the actuation of the clutch and shift mechanisms of the transmission. A Simulink model was developed of this system, and the hardware and software basis for an on-car controller was designed and implemented. Additionally, driver interactions with the system have been detailed, and advanced controller functions designed.

  \item The first iteration of a braking module was designed and implemented allowing electronic control of the vehicles brake bias.

  \item A multiplexing telemetry module was designed and implemented allowing multiple data source on the vehicle to stream data to their proprietary PC software.

  \item The first iteration of a dynamic driver interface module was designed and implemented that allows drivers to control vehicle parameters at runtime.
  
\end{itemize}

\section{Recommendations for Future Work}

To further the goals set out in Ch.\ \ref{cha:goals}, and to generally improve upon what was accomplished during this project, the following items have been identified as recommendations for future work:

\subsection{Engine and Transmission}

Several engine and transmission goals are not realizable until the vehicle has been constructed. Once constructed, future work includes:

\begin{itemize}
  \item Identification of the model parameters within the actual electro-pneumatic system;
  \item Development of the electro-pneumatic controlling algorithms;
  \item Physical implementation of the electro-pneumatic actuation system;
  \item Physical implementation of the variable intake actuator.
\end{itemize}

\subsection{Braking}

The brake module has yet to be tested with the brake pedal assembly, as it has not yet been fabricated. Future work includes testing the bias adjustment and calibration procedures with the actual balance bar.

\subsection{Telemetry}

The telemetry module has yet to be field tested to determine if it meets the range requirements proposed. Future work includes testing the range of the telemetry module and its noise resilience at the Formula SAE competitions.

\subsection{Driver Interface}

At the time of project completion, the steering wheel had not yet been manufactured by the team. Two major targets remain for the driver interface:

\begin{itemize}
	\item Completion of the user interface and vehicle dynamic manager software; and
	\item Testing of the user interface with the other modules while mounted to the vehicle.
\end{itemize}
