\section{Driver Interface Module Design\label{sec:Driver-Interface-Module}}


\subsection{Purpose}


\subsection{Processes}


\subsubsection{Driver Controls}
The driver controls consist of three rotary encoder knobs and three buttons. See table \ref{table:driver_controls} for a description of each.

\begin{table}[H]
\caption{Available driver controls.\label{table:driver_controls}}
\centering
\begin{tabular}{|c|c|p{8 cm}|}
	\hline 
	Type & Name & Description \\
	\hline
	\hline 
	Rotary & VDM & Changes the current VDM setting. \\
	\hline 
	Rotary & Option & Changes the currently selected menu option. \\
	\hline
	Rotary & Adjust & Adjusts the value associated with the currently selected menu option. \\
	\hline
	Button & Starter & Engages the automatic start sequence if pressed once, or the manual start sequence if held down.\\
	\hline
	Button & Neutral Find & Activates the neutral-find feature. \\
	\hline
	Button & Diagnostics/Save & Pages through diagnostic information if pressed once, or saves the current dynamic settings to the selected VDM if held down.\\		
	\hline 		
\end{tabular}
\end{table}


\subsubsection{Diagnostic Information}

The interface display panel is a large monochrome \emph{Liquid Crystal Display} (LCD) screen, inset into the steering wheel. The panel provides real-time information to the driver regarding all of the electronic systems in the car. Primary information displayed on the panel includes:

\begin{itemize}
\item the selected gear;
\item the active \emph{vehicle dynamics mode} (VDM);
\item the telemetry signal strength;
\item the engine RPM;
\item the vehicle wheel speed; and
\item the status of the launch control feature.
\end{itemize}

The list of available options and the current value for the selected option is displayed on screen when the driver rotates the option dial. After a timeout period, normal real-time information display resumes. 



\subsubsection{Vehicle Dynamics Mode (VDM)}
\nomenclature{VDM}{Vehicle Dynamics Mode}

The driver interface system provides a method of quickly modifying several dynamic vehicle parameters quickly and easily. For example, an acceleration event calls for launch control, auto-upshift, and a heavy forward brake bias. It is possible to enable all of these features in one step by changing the VDM mode to {}``acceleration''. 

When a new mode is selected, all nodes on the network are notified and synchronized to modify their dynamic parameters in accordance with the specific mode. For example, when the  {}``acceleration'' mode is enabled, the engine module will enable launch control and auto-upshift, and the brake controller will modify the brake bias to a pre-set ratio.

\begin{description}
  \item [{Pit Mode}] enables soft-launch driving characteristics that mimic a fully automatic transmission. This makes slowly driving the car forward from a stand-still far easier, and only requires the driver to take their left foot off the brake, and slightly apply the throttle.
  \item [{Acceleration Mode}] puts the vehicle systems into full-performance characteristics. Launch control is activated. The engine module will watch for a launch signal from the driver, and will automatically up-shift based on the engine RPM.
  \item [{Dynamic Mode}] puts the vehicle systems into a mode that is suitable for the autocross, and the endurance race.
\end{description}


\subsubsection{Parameter Tuning}


\subsection{Software}


\subsubsection{User Interface Manager}


\subsubsection{Driver Control Manager}


\subsubsection{Vehicle Diagnostics Manager}


\subsubsection{Vehicle Dynamic Mode Manager}


\subsubsection{I/O Monitor}


\subsubsection{CAN Interface}


\subsubsection{Main Control Loop}


\subsection{Hardware}


\subsubsection{Microcontroller}


\subsubsection{CAN Transceiver}


\subsubsection{LCD Module}


\subsubsection{Input Knobs and Buttons}


\subsubsection{Paddle Shifters}