\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

We would like to acknowledge the assistance, support, knowledge, and hard-work of the many people that made this project possible. We could never hope to succeed with a project of this scope without a dedicated group of professionals to support us.

First and foremost, we would like to acknowledge the skill and hard work of the University of Manitoba Formula SAE team. Without the dedication and talent of these student engineers, we would have no vehicle to design for. It is a great honour and pleasure to work with them.

We would like to acknowledge the mentorship and leadership provided by our thesis advisor Dr. Witold Kinsner. His insistence on being the best gave us strength while we were struggling to avoid cutting corners. We hope to carry on the spirit of professionalism and attention to detail he has imparted on us. 

We would also like to acknowledge Dr. Dean McNeill for his guidance throughout the project, and his generosity with his own lab equipment. We found the debugging tools he lent us to be invaluable to our implementation.

Many thanks and kudos to Alan Forbes for his valuable input on our technical writing. His insistence on conciseness and readability have been a guiding principle for our technical writing. 

As mentioned in our contributions page, Sinisa Janjic and Zoran Trajkoski of the ECE Tech Shop helped our debugging process immensely, and have saved a great deal of our time and sanity. Their contribution greatly improved the quality of our physical implementation.

Finally, we would like to acknowledge the generous donations of three key project sponsors: Alberta Printed Circuits, for manufacturing our printed circuit boards free of charge, Newhaven Electronics, for supplying the LCD module used for our driver interface, and Optimum Electronics, for giving us the development board used to create the CAN packet injector. 
