\chapter{Results and Discussion}
\label{cha:results}

This purpose of this chapter is to describe the testing procedures, results, and implementation issues that were encountered during the implementation phase of the project. Whenever possible, concrete results will be compared with those described previously in Ch.\ \ref{cha:goals}. The amount of work accomplished with each module will also be discussed.

The Engine and Transmission, and Braking modules both require that the Formula SAE 2010 vehicle be at least partly complete for testing. Since the build schedule for the vehicle is to have it complete for the beginning of May, 2010, much of the final-stage testing and tuning of these modules was not yet possible as of writing. Additionally, a prototype of the full pneumatics system was not ready at the time of writing.

\input{results/results_transmission.tex}

\input{results/results_braking.tex}

\input{results/results_telemetry.tex}

\input{results/results_driver_interface.tex}

\section{Implementation Issues Encountered}

Several specific implementation issues caused a lot of headaches and project delays. All of these issues were subsequently solved.

\subsection{CAN Transceiver Hardware Bug}

After the first module was populated, we proceeded to inspect all solder joints and check for shorts between VCC and ground. Initially no problems were apparent, but when we first applied power to the module, using a current limiting bench power supply, a dynamic short circuit quickly appeared. The power supply immediately began limiting current, and the voltage dropped.

After a lot of searching, inspecting all the components under a microscope, and hot air rework, it was determined that the problem was not with any of the solder joints or the PCB, but in fact a problem with the schematic. In error, the circuit design for the CAN transceiver had got the VCC and GND lines to the chip swapped. Additionally, this CAN Transceiver schematic block had been duplicated to all four modules, which resulted in the same fate for each module.

A fix was quickly implemented, first on the engine and transmission module, and subsequently for the other modules. The copper traces to the VCC and GND pins on the CAN Transceiver were cut with an X-ACTO knife, and rewired correctly with wire-wrap wire.

\subsection{Driver Interface LCD Reset Line}

After populating the driver interface module, an issue persisted with the active low reset line that prevented the LCD Module from being pulled out of reset with the rest of the system. Upon probing the reset line on the LCD with an oscilloscope, it was found to be oscillating at \unit{60}{\mega\hertz}. Because the LCD module uses \unit{+3.3}{\volt} logic, reset line was isolated from the rest of the system with a direction-sensing level shifter. It is hypothesized that some circuitry on the LCD module was attempting to drive the reset line, and this was causing the oscillations. Adding a (\unit{120}{\ohm}) pull-up resistor to the LCD module's reset line solved the issue. 

\subsection{Telemetry Module Software Race Conditions}

Multiple race conditions were caused by the large degree of asynchronous behaviour in the system, the large number of common resources used, and the multiple producer/consumer layers. These issues appeared in code that had been in use for a while on other modules, but only caused problems on the Telemetry Module. The majority of these were solved by ensuring that atomic sections were placed around critical code.

\subsection{Telemetry Module Interrupt Starvation}

Although initial average data throughput rates for both the DAQ and the ECU were measured as part of the research done at the beginning of the project, non-trivial buffering issues did arise in the implementation of the telemetry module software. After several weeks of work spent debugging throughput problems with the module software, and with the aide of a protocol analyzer, the root of the problem was tracked down. The AT90CAN micro-controller's interrupt vectors are fixed at the factory, therefore the priority of interrupts on the micro-controller is fixed. Unfortunately this lead to a resource starvation issue. The MAX3100 UART uses an external interrupt line, which has priority over the internal UART interrupts. When there is data in the MAX3100's transmit buffer, the MAX3100's interrupt handler will starve the internal UART interrupt to a certain extent. This was investigated by saturating the MAX3100 output buffer with a constant stream of data, and then inputting some bytes to the internal UART. Single input bytes were read properly, but any long stream of incoming bytes (more than 4 in a row) would cause hardware input buffer overruns in the built-in UART, and incoming data would be lost.

\begin{figure}[ht]
  \centering
  \label{fig:ecu_data}
  \begin{tikztimingtable} %[timing/nice tabs]
    $ECU_{Rx}$ & Z 10D{Polling sequence (7 bytes)} 14F Z \\
    $ECU_{Tx}$ & 12Z 6D{Reply sequence} ;[dotted] 2D{...}; 5D{(539 bytes)} Z\\
    \extracode
      %\tableheader{Signal}{Timing}
      \tablerules
  \end{tikztimingtable}
  \caption{Timing diagram for the ECU Serial Data Example}
  \label{fig:ecu_serial_data}
\end{figure}

Based on this knowledge, we were able to classify conditions where the software would be unable to accurately process the incoming data. Unfortunately the method that the ECU transmits its data falls within this characterization. When the ECU is communicating with the DTASWin software, the software will send a handful of bytes (around 7) to the ECU, and the ECU will respond with one large packet of approximately 540 bytes, as shown in Fig.\ \ref{fig:ecu_serial_data}. If the MAX3100 is transmitting a large amount of data when this large packet comes in, bytes will be lost from the interrupt starvation issue.

Having determined the problem, several options lay before us to resolve the issue:
\begin{itemize}
  \item By lumping the ISR handlers for both the internal UART and the MAX3100 together, it would be possible to conditionally alter the priority of the processing to allow the incoming data to take precedence. This would however override the natural encapsulation that the two drivers had, and would require writing specialized drivers for use only on the telemetry module;
  \item Throttling the transmission of data to the MAX3100 by sequenced enabling and disabling of the interrupt could also reduce the starvation issue, but getting the sequencing and timing right would be difficult and more than likely result in further problems;
  \item Finally, the method successfully used in the implementation was to enabled nested interrupts from the MAX3100 interrupt handler. This is done in two steps at the beginning of the interrupt handler: First, the MAX3100 external interrupt is disabled, to prevent it recursively firing. Second, global interrupts are re-enabled. This allows the UART to interrupt the MAX3100 interrupt when it receives a byte.
\end{itemize}
